---
title: "Monitor model"
output: 
  vetiver::vetiver_dashboard:
    pins:
      board: !expr pins::board_url(c(chicago_model = "https://colorado.posit.co/rsc/chicago-rstats-model-pin/"))
      name: 'chicago_model'
      version: NULL
    storyboard: true
    theme: 
      version: 4
      bootswatch: cosmo
    display_pins: true
---

```{r setup, include = FALSE}
library(flexdashboard)
library(vetiver)
library(pins)
library(plotly)
library(arrow)

knitr::opts_chunk$set(echo = FALSE)
pins <- get_vetiver_dashboard_pins()
```

```{r load-vetiver-model, include = FALSE}
# Load deployed model from pin:
v <- vetiver_pin_read(pins$board, pins$name, version = pins$version)
meta <- pin_meta(pins$board, pins$name, version = pins$version)
days_old <- difftime(Sys.Date(), as.Date(meta$created), units = "days")

# Attaches packages needed for prediction:
attach_pkgs(v$metadata$required_pkgs)
```

```{r validation, include = FALSE}
# Load new validation data, for example from database or API:
path <- here::here("data", "inspections_monitoring.parquet")
validation_df <- read_parquet(path)
validation_aug <- augment(v, validation_df) |> 
  mutate(.pred_class = as.factor(.pred_class))

new_metrics <-
  validation_aug |>
  vetiver_compute_metrics(inspection_date, "month", results, .pred_class)
```


### Model metrics

```{r}
p1 <- new_metrics |>
  vetiver_plot_metrics() + 
  ## you can also operate on the ggplot:
  scale_size(range = c(2, 5))

p1 <- ggplotly(p1)
hide_legend(p1)
```

***

This model was published `r as.numeric(days_old)` days ago.

Plot model metrics over time to *monitor* your model.

### Explore validation data

```{r}
p2 <- validation_df |> 
  ggplot(aes(total_violations, after_stat(density), fill = results)) +
  geom_histogram(alpha = 0.7, position = "identity")

ggplotly(p2)
```


***

Write your own code to make visualizations or tables with the new validation data, and/or the new predictions.

### API visual documentation

```{r echo=FALSE, out.width="100%"}
## use your own vetiver model API URL here:
knitr::include_url("https://colorado.posit.co/rsc/chicago-inspections-rstats/", height = "600px")
```

***

Interact directly with your model via its visual documentation, and get `curl` examples.

