---
title: "4 - Monitor your model"
subtitle: "Deploy and maintain models with vetiver"
format:
  revealjs: 
    slide-number: true
    footer: <https://posit-conf-2023.github.io/vetiver>
    preview-links: auto
    incremental: true
    theme: [default]
    width: 1280
    height: 720
knitr:
  opts_chunk: 
    echo: true
    collapse: true
    comment: "#>"
---

```{r}
#| include: false
#| file: setup.R
```

::: r-fit-text
We made it! 🎉
:::

## Your turn 🏺 {transition="slide-in"}

*What is one thing you learned that surprised you?*

*What is one thing you learned that you plan to use?*

```{r}
#| echo: false
library(countdown)
countdown(minutes = 5)
```

## Resources to keep learning

-   Documentation at <https://vetiver.rstudio.com/>

-   Isabel's talk from rstudio::conf() 2022 on [Demystifying MLOps](https://www.rstudio.com/conference/2022/talks/demystifying-mlops/)

-   [Webinar by Julia and Isabel](https://juliasilge.github.io/mlops-rstudio-meetup/) for Posit Enterprise Meetup

-   End-to-end demos from Posit Solution Engineering in [R](https://github.com/sol-eng/bike_predict) and [Python](https://github.com/sol-eng/bike_predict_python)

-   Are you on the right track with your MLOps system? Use the rubric in ["The ML Test Score: A Rubric for ML Production Readiness and Technical Debt Reduction"](https://research.google/pubs/pub46555/) by Breck et al (2017)

. . .

Follow Posit and/or us on your preferred social media for updates!

# Submit feedback before you leave 🗳️

[feedback-url-goes-here](tktk)

Your feedback is crucial! Data from the survey informs curriculum and format decisions for future conf workshops and we really appreciate you taking the time to provide it.
